---
title: "RWorksheet_asenjo#4c"
author: "Samuel Asenjo"
date: "2024-11-04"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. a.
```{r}

mpg <- read.csv("/cloud/project/Worksheet 4/mpg.csv")

```
b. The categorical variables in the data set are manufacturer, model name, type of transmission, drive type, fuel type, number of cylinders, and, vehicle class.

c.The continuous variables in the data set are displacement, year of manufacturing, city mileage, highway mileage.

2.1. 
```{r}
library(dplyr)
library(ggplot2)


manufacturer_count <- mpg %>%
  group_by(manufacturer) %>%
  summarise(model_count = n_distinct(model)) %>%
  arrange(desc(model_count))

top_manufacturer <- manufacturer_count[1, ]

model_variation <- mpg %>%
  group_by(model) %>%
  summarise(variation_count = n()) %>%
  arrange(desc(variation_count))

top_model <- model_variation[1, ]

top_manufacturer
top_model

```




a. 
```{r}
  mile <- mpg %>%
  group_by(manufacturer) %>%
  summarise(unique_models = n_distinct(model)) %>%
  arrange(desc(unique_models))
mile

```
b. 
```{r}
library(dplyr)
barplot(mile$unique_models, 
        names.arg = mile$manufacturer, 
        col = "lightblue",
        main = "Unique Models per Manufacturer", 
        xlab = "Manufacturer", 
        ylab = "Number of Unique Models",
        las = 2,          
        cex.names = 0.7)
```
```{r}
library(ggplot2)

ggplot(mile, aes(x = manufacturer, y = unique_models)) +
  geom_bar(stat = "identity", fill = "lightblue") +
  ggtitle("Unique Models per Manufacturer") +
  xlab("Manufacturer") +
  ylab("Number of Unique Models") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 10))  

```

2.2. a. The code The plot created by ggplot(mpg, aes(model, manufacturer)) + geom_point() is a scatter plot that shows the relationship between car manufacturers (y-axis) and their models (x-axis), with each point representing a specific model from a manufacturer. It visually displays which models belong to which manufacturer, but due to many categorical values, it can appear crowded.
```{r}
ggplot(mpg, aes(model, manufacturer)) + geom_point()
```
b. No, the original plot isn't very useful because it is overcrowded and doesn't offer clear insights with categorical data on both axes. A better approach would be to group the data by manufacturer, count the number of unique models, and create a bar plot to show how many models each manufacturer produces.


3. 
```{r}
library(ggplot2)
library(dplyr)


mpg_top20 <- mpg %>% head(20)

ggplot(mpg_top20, aes(x = model, y = year)) +
  geom_point(color = "blue", size = 3) +
  labs(title = " Model vs Year (Top 20 Observations)", 
       x = "Model", 
       y = "Year") +
  theme_minimal()

```
4. 
```{r}
library(dplyr)
library(ggplot2)


cars_per_model <- mpg %>%
  group_by(model) %>%
  summarise(car_count = n()) %>%
  arrange(desc(car_count))

cars_per_model

```
a. 
```{r}
library(ggplot2)
library(dplyr)



mpg_top20 <- mpg %>% head(20)

model_counts <- mpg_top20 %>%
  group_by(model) %>%
  summarise(car_count = n()) %>%
  arrange(desc(car_count))

ggplot(model_counts, aes(x = reorder(model, -car_count), y = car_count, fill = model)) +
  geom_bar(stat = "identity") +
  labs(title = "Car Count per Model (Top 20 Observations)",
       x = "Car Model", 
       y = "Count of Cars") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_manual(values = rainbow(nrow(model_counts)))

```
b. 
```{r}
library(ggplot2)
library(dplyr)


model_counts <- mpg %>%
  group_by(model) %>%
  summarise(car_count = n()) %>%
  arrange(desc(car_count))

ggplot(model_counts, aes(x = reorder(model, car_count), y = car_count, fill = model)) +
  geom_bar(stat = "identity") +
  coord_flip() +  # Flips the coordinates to make horizontal bars
  labs(title = "Number of Cars per Model", 
       x = "Car Model", 
       y = "Count of Cars") +
  theme_minimal() +
  theme(legend.position = "none") +  # Hide the legend
  scale_fill_manual(values = rainbow(nrow(model_counts)))

```
5. a. The relationship between the number of cylinders and engine displacement is generally positive, meaning that as the number of cylinders increases, the engine displacement tends to increase as well. This suggests that cars with more cylinders typically have larger engines in terms of displacement.

```{r}
library(ggplot2)


ggplot(mpg, aes(x = cyl, y = displ, color = displ)) +
  geom_point(size = 3) +
  labs(title = "Relationship between No. of Cylinders and Engine Displacement",
       x = "Number of Cylinders",
       y = "Engine Displacement (Liters)",
       color = "Engine Displacement") +
  theme_minimal()

```
6.1. The scatter plot reveals a negative correlation between engine displacement (displ) and highway miles per gallon (hwy), indicating that as engine displacement increases, highway MPG tends to decrease. This output arises because larger engines typically consume more fuel, leading to lower fuel efficiency on the highway, reflecting the trade-off between engine size and fuel economy in vehicles.

```{r}
library(ggplot2)



ggplot(mpg, aes(x = displ, y = hwy, color = displ)) +
  geom_point(size = 3, alpha = 0.7) +
  labs(title = "Relationship between Engine Displacement and Highway MPG",
       x = "Engine Displacement (Liters)",
       y = "Highway MPG",
       color = "Engine Displacement") +
  theme_minimal()

```
6.2. 
```{r}
traffic <- read.csv("/cloud/project/Worksheet 4/traffic.csv")


```
a. 
```{r}

num_observations <- nrow(traffic)
print(paste("Number of observations:", num_observations))

variables <- colnames(traffic)
print("Variables in the dataset:")
print(variables)

```
b. 
```{r}


junction_subsets <- split(traffic, traffic$Junction)


```
```{r}
library(ggplot2)
library(dplyr)


traffic$DateTime <- as.POSIXct(traffic$DateTime, format="%Y-%m-%d %H:%M:%S")

ggplot(traffic, aes(x = DateTime, y = Vehicles, color = factor(Junction))) +
  geom_line() +
  labs(title = "Traffic Volume Over Time by Junction",
       x = "Date and Time",
       y = "Number of Vehicles",
       color = "Junction") +
  theme_minimal() +
  facet_wrap(~ Junction, scales = "free_y")

```
7. 
```{r}
library(readxl)

alexa <- read_excel("/cloud/project/Worksheet 4/alexa_file.xlsx")

```

a. 
```{r}
n <- nrow(alexa)
print(paste("Number of observations:", n))

v <- colnames(alexa)
print("Variables in the dataset:")
print(variables)
```
b. 
```{r}
library(dplyr)


variation_counts <- alexa %>%
  group_by(variation) %>%
  summarise(total = n())

print(variation_counts)

```
c. The plot shows which product variations are most popular, with a clear lead for some variations over others. It highlights consumer preferences for specific variations in the data.

```{r}
ggplot(variation_counts, aes(x = reorder(variation, -total), y = total, fill = variation)) +
  geom_bar(stat = "identity") +
  labs(title = "Count of Each Product Variation",
       x = "Product Variation",
       y = "Total Count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  guides(fill = FALSE)
```
d. 
```{r}
alexa$date <- as.Date(alexa$date)

daily_reviews <- alexa %>%
  group_by(date) %>%
  summarise(total_verified_reviews = sum(feedback))

ggplot(daily_reviews, aes(x = date, y = total_verified_reviews)) +
  geom_line(color = "blue") +
  labs(title = "Number of Verified Reviews Over Time",
       x = "Date",
       y = "Total Verified Reviews") +
  theme_minimal()
```
e. 
```{r}
library(dplyr)
library(ggplot2)

variation_ratings <- alexa %>%
  group_by(variation) %>%
  summarise(average_rating = mean(rating, na.rm = TRUE)) %>%

arrange(desc(average_rating))

variation_ratings
```


```{r}
hv <- variation_ratings %>%
  slice(1)
hv
```


```{r}
ggplot(variation_ratings, aes(x = reorder(variation, -average_rating), y = average_rating, fill = variation)) +
  geom_bar(stat = "identity") +
  labs(title = "Average Rating by Product Variation",
       x = "Product Variation",
       y = "Average Rating") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  guides(fill = FALSE)
```

