---
title: "RWorksheet_asenjo#4b"
author: "Samuel Asenjo"
date: "2024-10-28"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. 
```{r}

vectorA <- c(1, 2, 3, 4, 5)


matrixA <- matrix(0, nrow = 5, ncol = 5)


for (i in 1:5) {
  for (j in 1:5) {
    matrixA[i, j] <- abs(i - vectorA[j])
  }
}

print(matrixA)

```

2. 
```{r}
v <- c(1, 2, 3, 4, 5)

for(i in v){
  cat(rep("*", i),"\n")
}
```


3. 
```{r}
start_num <- as.integer(readline(prompt="Enter the starting number for the Fibonacci sequence: "))

```


```{r}
a <- 0
b <- 1
if (!is.na(start_num) < 0) {
1
cat("Please enter a non-negative starting number.\n")
} else {
repeat {
if (!is.na(start_num) && a >= start_num) {
cat(a, "\n")
}
temp <- a + b
a <- b
b <- temp
if (!is.na(start_num) && a > 500) {
break
}
}
}




```
4. a.
```{r}
Shoesizes <-read.csv("/cloud/project/Worksheet 4/shoesizes.csv")

head(Shoesizes)

```

b. 
```{r}
male_data <- subset(Shoesizes, Gender == "M")
female_data <- subset(Shoesizes, Gender == "F")

num_males <- nrow(male_data)
num_females <- nrow(female_data)

cat("Number of observations for Male: ", num_males, "\n")
cat("Number of observations for Female: ", num_females, "\n")
```

c. 
```{r}
library(ggplot2)

HouseHoldData <-read.csv("/cloud/project/Worksheet 4/HouseholdData.csv")


ggplot(HouseHoldData, aes(x=Sex, fill=Sex)) +
  geom_bar() +
  ggtitle("Number of Males and Females in Household Data") +
  xlab("Gender") +
  ylab("Count") +
  scale_fill_manual(values = c("blue", "pink")) +
  theme_minimal()

```


5. 
```{r}
expenses <- c(Food = 60, Electricity = 10, Savings = 5, Miscellaneous = 25)

percentages <- round(100 * expenses / sum(expenses), 1)

labels <- paste(names(expenses), percentages, "%")

colors <- c("lightblue", "lightgreen", "yellow", "pink")

pie(expenses, labels = labels, col = colors, main = "Dela Cruz Family Monthly Expenses")

```


6. 
```{r}
data(iris)
```

a. The output shows number of variables and objects, and rows and columns
```{r}
str(iris)
```
b. 
```{r}


means <- colMeans(iris[, c("Sepal.Length", "Sepal.Width", "Petal.Length", "Petal.Width")])

means

```
c. 
```{r}


species_distribution <- table(iris$Species)

colors <- c("blue", "green", "yellow")

pie(species_distribution, 
    main = "Distribution of Iris Species", 
    col = colors, 
    labels = paste(names(species_distribution), "(", species_distribution, ")", sep=""))

legend("topright", legend = names(species_distribution), fill = colors, title = "Species")

```

d. 
```{r}

setosa <- subset(iris, Species == "setosa")
versicolor <- subset(iris, Species == "versicolor")
virginica <- subset(iris, Species == "virginica")

 tail(setosa)
 tail(versicolor)
 tail(virginica)

```
e. 
```{r}
iris$Species <- as.factor(iris$Species)

colors <- c("setosa" = "blue", "versicolor" = "green", "virginica" = "red")
symbols <- c("setosa" = 16, "versicolor" = 17, "virginica" = 18)

plot(iris$Sepal.Length, iris$Sepal.Width, 
     col = colors[iris$Species],           
     pch = symbols[iris$Species],          
     xlab = "Sepal Length",                
     ylab = "Sepal Width",                 
     main = "Iris Dataset",                
     sub = "Sepal width and length",       
     cex = 1.5)                            

legend("topright", legend = levels(iris$Species), 
       col = c("blue", "green", "red"), 
       pch = c(16, 17, 18), 
       title = "Species")

```
f. The scatterplot shows clear separation between setosa and the other two species based on Sepal Length and Sepal Width. Setosa has distinctively shorter and wider sepals, forming a separate cluster. Versicolor and virginica overlap more, particularly in sepal width, but virginica tends to have longer sepals. Overall, there is a slight negative correlation, where longer sepals tend to be narrower, especially in virginica.